---
title: "DimpleKanadia-ANLY512-50-VI-2016"
author: "Dimple Kanadia"
date: "July 25, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Data Import & Cleanup
```{r, echo=TRUE}
library(dplyr)  # for easy filtering
library(ggplot2)
library(datasets)

dat <- read.csv("movie_data.csv")#Import csv
str(dat)#Check structure of the data frame

# Clean up some variables
dat$Domestic <- as.numeric(dat$Domestic) #Convert these columns to numeric
dat$Worldwide <- as.numeric(dat$Worldwide)
dat$International <- as.numeric(dat$International)
dat$AVG.rating <- as.numeric(dat$AVG.rating)


dat2 <- filter(dat, Title.type == "Feature Film")
```


### Multi-step Visualization

Look at the distribution of earnings by release year.
```{r, echo=TRUE}
ggplot(dat2, aes(Year, Worldwide)) +
  geom_bar(stat = "identity")
```

Lots of empty year earlier on, I will try just domestic earnings.
```{r, echo=TRUE}
ggplot(dat2, aes(Year, Domestic)) +
  geom_bar(stat = "identity")
```

No similar patterns.  Looks like missing data early in the time series.

```{r, echo=TRUE, fig.width=20}
dat3 <- filter(dat2, Year >= 1990)

ggplot(dat3, aes(factor(Year), Domestic)) +
  geom_bar(stat = "identity") +
  ggtitle("Annual Domestic Movie Earnings") +
  ylab("Domestic Earnings (USD)") +
  xlab("Year")
```
## Movies released in 21 century had collected higher revenue in USA.

## Look for International earnings yearly
```{r, echo=TRUE, fig.width= 20}
  
  ggplot(dat3, aes(factor(Year), International))+ 
  geom_bar(stat = "identity", fill="#FF9999", colour="#FF9999") +
  ggtitle("Annual International Movie Earnings") +
  ylab("International Earning (USD)") +
  xlab("Year")
```
## Movies released in year 2012 made the maximum earnings internationally


## Look for Worldwide earnings yearly
```{r, echo=TRUE, fig.width= 20}
  
  ggplot(dat3, aes(factor(Year), Worldwide))+ 
  geom_bar(stat = "identity", fill="#000099", colour="#000099") +
  ggtitle("Annual Worldwide Movie Earnings") +
  ylab("Worldwide Earning (USD)") +
  xlab("Year")
```

## Look for Average Rating of movies on Year of Release
```{r, echo=TRUE, fig.width= 10}
  ggplot(dat3, aes(released, AVG.rating))+ 
  geom_bar(stat = "identity", fill="#CC79A7", colour="#CC79A7") +
  ggtitle("Average Rating with Released Year of Movies") +
  ylab("Average rating") +
  xlab("Year of Release")
```
## Average ratings of movies released in 2005-2008 is very low.It also dropped drastically in 2011



